Response to the defense feedback

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

        \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
        \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;
        \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b2);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a4) -- (b2);
      \end{tikzpicture}
    }
    \caption*{(b) Noiseless Loss}
  \end{minipage}
  \caption{Two Kinds of Channels}\label{fig:channel}
\end{figure}

@@

\begin{myexample}
Suppose we sample a program from $k_1$ to $k_8$ and record memory accesses at the granularity of one byte from $\mathtt{7ffff7ffd000}$ to $\mathtt{7ffff7ffd03f}$ (one cache line). We perform a bit-wise operation of each address within the range. Because the cache line is always accessed. It is not a leak here.
\begin{center}
  \begin{tabular}{c}
    {
      \begin{lstlisting}[frame=none]
              k1  k2  k3  k4  k5  k6  k7  k8   Result  
7ffff7ffd000   1   0   1   0   1   1   0   1 
7ffff7ffd000   0   1   1   0   1   1   1   1 
7ffff7ffd000   1   1   1   1   1   1   0   1 
7ffff7ffd000   1   0   1   0   1   1   1   1 
...
7ffff7ffd03f   1   0   1   0   1   1   1   0  
cache line     1   1   1   1   1   1   1   1    0 (No Leaks)
\end{lstlisting}
    }
  \end{tabular}
\end{center}
\end{myexample}

@@

      \begin{tabular}{ll}
        \toprule
        Observation & P     \\
        \midrule
        00          & $3/8$ \\
        01          & $1/2$ \\
        10          & 0     \\
        11          & $1/8$ \\
        \bottomrule
      \end{tabular}
    }
  \end{minipage}
  \caption{Example 2}\label{fig:design:example2}
\end{figure}
\end{myexample}

>>>>

        \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
        \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;
        \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b2);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a4) -- (b2);
      \end{tikzpicture}
    }
    \caption*{(b) Noiseless Loss}
  \end{minipage}
  \caption{Two kinds of information channels}\label{fig:channel}
\end{figure}

@@

\begin{myexample}
Suppose we sample a program from $k_1$ to $k_8$ and record memory accesses at the granularity of one byte from $\mathtt{7ffff7ffd000}$ to $\mathtt{7ffff7ffd03f}$ (one cache line). We perform a bit-wise operation of each address within the range. Because the cache line is always accessed. It is not a leak here.
\begin{center}
  \begin{tabular}{c}
    {
      \begin{lstlisting}[frame=none,numbers=none]
              k1  k2  k3  k4  k5  k6  k7  k8   Result  
7ffff7ffd000   1   0   1   0   1   1   0   1 
7ffff7ffd000   0   1   1   0   1   1   1   1 
7ffff7ffd000   1   1   1   1   1   1   0   1 
7ffff7ffd000   1   0   1   0   1   1   1   1 
...
7ffff7ffd03f   1   0   1   0   1   1   1   0  
cache line     1   1   1   1   1   1   1   1    0 (No Leaks)
\end{lstlisting}
    }
  \end{tabular}
\end{center}
\end{myexample}

@@

      \begin{tabular}{ll}
        \toprule
        Observation & P     \\
        \midrule
        00          & $3/8$ \\
        01          & $1/2$ \\
        10          & 0     \\
        11          & $1/8$ \\
        \bottomrule
      \end{tabular}
    }
  \end{minipage}
  \caption{We estimate the amount of leaked information by traversing a binary tree.}\label{fig:design:example2}
\end{figure}
\end{myexample}
